---
title: "MBA 563 Template For Assignment 3"
author: "Arindam Roy(arindam6)"
date: "`r as.character(Sys.time())`"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
```

# 1 - Load data 

```{r}
df <- read.csv("store_3HE.csv", stringsAsFactors = F)
```

# 2 - Familiarization with the data 

```{r}
summary(df)
```
```{r}
n_distinct(df)
```


```{r}
str(df)
```
```{r}
head(df)
```
There are 20 columns and 771 records in the dataset.

# 3 - Convert __revenue__ to numeric 
```{r}
df$revenue <- as.numeric(df$revenue)
str(df)
```
```{r}
summary(df$revenue)
```
```{r}
colSums(is.na(df))
```
```{r}
which(is.na(df), arr.ind=TRUE)
which(is.na(df$size), arr.ind=TRUE) 
which(is.na(df$revenue), arr.ind=TRUE)
```
```{r}
df_na_size <- subset(df, is.na(df$size))
df_na_revenue <- subset(df, is.na(df$revenue))
df_na_size
df_na_revenue
```


# 4 - Delete rows with missing values
```{r}
df <- df %>% drop_na()
```

```{r}
n_distinct(df)
```
```{r}
mean(df$revenue)
```


Exploratory Data Analysis Tasks. 


# 5 - df_low and df_high


```{r}

df_high <- df[df$revenue >= ave(df$revenue) , ]
#n_distinct(df_high)
mean(df_high$revenue)
mean(df_high$size)
```
```{r}
df_low <- df[df$revenue < ave(df$revenue) , ]
#n_distinct(df_low)
mean(df_low$revenue)
mean(df_low$size)
```
```{r}

ggplot(df_low, aes(x = size, y = revenue)) +
    geom_point()
```
```{r}
ggplot(df_high, aes(x = size, y = revenue)) +
    geom_point()

```




When the revenue is less than the average revenue in the dataset there is a strong correlation between revenue and size, i.e. revenue is increased when the size is also increasing, but if it is other way, the relationship is not so strong.

# 6 - Correlation betweeen __revenue__ and __size__  

```{r}
cor(df$revenue, df$size)
```


```{r}
ggplot(df, aes(x = size, y = revenue)) +
    geom_point()
```



# 7 - Boxplots of __revenue__ for each region 
```{r}
ggplot(df) +
  geom_boxplot(aes(x = region, y = revenue)) 
```



It is observed from the chart that WEST region has highest median sales and there are few outliers are also present in the dataset. Ontario region has minimum 25% and 75% quartile range of revenue among all the regions.

# 8 - Bar chart of __gross_profit__ for each province  
```{r}
df %>% 
  ggplot(aes(x = province)) +
  geom_bar() +
  labs(y = "gross_profit", x = "province")
```



It is observed from the chart that ON province has highest gross profit collected and NB and PE are lowest gross profit province.

# 9 - Correlation matrix of average store sales for product categories  
```{r}
df_corr <- df %>%
  select(promo_units, energy_units, regularBars_units, gum_units, bagpegCandy_units, isotonics_units, singleServePotato_units, takeHomePotato_units, kingBars_units, flatWater_units, psd591Ml_units) %>%
  cor()
df_corr
```
```{r}
sort(df_corr[df_corr!=max(df_corr)])
```


1) promo_units and isotonics_units are sold together most.

2) gum_units and psd591Ml_units are sold together least.