************************************************************************
# Title: In-Class Notebook Mod8HE K-Means DBSCAN
Course: MBA563
Term: Fall 2023
Mooc or HE?: HE
Module: 08
Author: Kim Mendoza and Jessen Hobson
************************************************************************

**********K-MEANS ***************************

__1.0 - Load and prep the data__
# Install packages and read in data
```{r}
#install.packages('tidyverse') #only install once
library(tidyverse)
#install.packages('factoextra') #only install once
library(factoextra)

# read in data (change to your path)
clustering_input1 <- read_rds(r"(C:\Users\kimendoz\Documents\MBA 563\Module 8 Live Session\clustering_input1.rds)")
```





























# remove store from the data for use later
```{r}
clustering_input2 <- clustering_input1 %>% 
        select(-store)

str(clustering_input2)
summary(clustering_input2)
```

























# Z-score standardization
```{r}
clustering_input2 <- as.data.frame(scale(clustering_input2))
```

__QUESTION:__ All variables are numerical and scaled. Why?
































__2.0 - picking k__
# Find a suitable k using two different methods
```{r}
# Within-cluster sum of square method
set.seed(42)
factoextra::fviz_nbclust(clustering_input2, kmeans, method = "wss")
```

```{r}
# Silhouette approach
set.seed(42)
factoextra::fviz_nbclust(clustering_input2, kmeans, method = "silhouette")
```

























__3.0 - Run and evaluate k-means__
# Run the model
```{r}
set.seed(42)
clusters <- kmeans(clustering_input2, centers=4, iter.max=10, nstart=10)
```
Arguments:
* `centers`: number of centroids (k random (distinct) rows are chosen as the initial centers)
* `iter.max`: the maximum number of iterations allowed
* `nstart`: how many random start configurations are chosen (for example, nstart=10 will generate 10 initial random centroids and choose the best one for the algorithm)



























# Check the size of the k clusters
(Ideally, clusters are of similar size)
```{r}
clusters$size
```




























# Visualize the clustering
(Uses principal components to collapse the dimensions of the data down to two dimensions)
```{r}
fviz_cluster(clusters, clustering_input2,  geom = "point", show.clust.cent = TRUE, palette = "jco", ggtheme = theme_classic())
```
__QUESTION:__ Is this really 4 clusters or 2?
__QUESTION:__ Are there outliers that should not be captured?






























# A matrix indicating the mean values for each feature and cluster combination
```{r}
clusters$centers
```
__QUESTION:__ What should we name each cluster?










































__4.0 - put clusters back into the dataset and investigate individual stores__
# Add clusters to the original, un-standardized dataset and add labels
```{r}
clustering_input1$cluster <- clusters$cluster

clustering_input1 <- clustering_input1 %>% 
        mutate(cluster_labels = case_when(
                cluster==1 ~ 'Cluster 1', 
                cluster==2 ~ 'Cluster 2',
                cluster==3 ~ 'Cluster 3',
                cluster==4 ~ 'Cluster 4'))

slice_sample(clustering_input1, n=10)
```
__Question__: What can NANSE do with this data?






























**********DBSCAN**************************************************
__5.0__ 
# Run this code before you start
```{r}
#install.packages('dbscan') #only install once
library(dbscan)

# read in data (change to your path)
clustering_input1 <- read_rds(r"(C:\Users\kimendoz\Documents\MBA 563\Module 8 Live Session\clustering_input1.rds)")

clustering_input2 <- clustering_input1 %>% 
        select(-store)
```

# Standardize the data using z-score standardization. 
The features need to be continuous and standardized. Why?
```{r}
clustering_input2 <- as.data.frame(scale(clustering_input2))
```























# Run the DBSCAN algorithm
```{r}
set.seed(42)
clusters_db <- dbscan::dbscan(clustering_input2, eps = 3, minPts = 4)
```






























# Use the `table()` function to print the size of the clusters.
```{r}
table(clusters_db$cluster)
```
__QUESTIONS__: 
1. How many clusters are present? 
2. What does the “0 cluster" represent? 
3. Generally, we prefer clusters to be relatively equal in size. How equal are the clusters here? 


























__6.0 - Visualize the clusters__
# Visualize the clusters
```{r}
fviz_cluster(clusters_db, clustering_input2,  geom = "point", show.clust.cent = FALSE, palette = "jco", ggtheme = theme_classic())
```
