---
title: "HE5 Live Session Handout"
author: "Ron Guymon"
date: "11/8/2023"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T # Change this to False if you don't want to include the code
                      , message = F
                      , warning = F)
```
## Introduction

In this handout we will use the data analytic workflow/FACT framework to make predicitons about future sales. Our focus will be on data modeling. The steps and the details that we will focus on are listed next.

## Steps

1. __F__ rame a question: What are future sales predicted to be for a campaign?  
2. __A__ ssemble data: The data has already been gathered and cleaned.  
3. __C__ alculate results 
  * First using EDA: We have already removed missing values, and cleaned it up quite a bit; however, we will use EDA to understand univariate and bivariate relationships to reinforce the regression calculations.  
  * Second using regression: We will illustrate both backward elminiation and forward selection for creating models that we can use for prediction.  
4. __T__ ell others about the results: We will use the models to make predictions, and then plot the predictions on plot to help us identify the optimal allocation of sales dollars.  


## Load libraries and data

Let's first load the packages that we will use, read in the data, and look at its structure.

```{r}
library(tidyverse) # For lots of tidyverse packages and functions
library(magrittr) # For pipe symbol
library(GGally) # For nice looking pairplots
library(plotly) # For interactive plots like in Alteryx

# Read in data
df <- readRDS('adSpend.rds') # Fictitious data for illustrating regression concepts
str(df) # Structure
```

The adspend data is fictitious data that we will use to illustrate regression concepts. It consists of 426 observations and 5 variables. Here is a brief description about each column:

1. __sales__: The dollar value of sales for the duration of the associated ad campaigns.
2. __adSpendFacebook__: The dollar value spent on advertising on Facebook.
3. __adSpendInstagram__: The dollar value spend on advertising on Instagram.
4. __campaign__: The name of the advertising campaign. There are three different campaigns in this dataset.
5. __store__: The nominal name of the store.

### Check for missing values

Missing values:

```{r}
colSums(is.na(df))
```

There are no missing values.

### Cardinality of Campaign and Store  

Let's get an idea of how many unique values there are for each campaign and store.

```{r}
summary(factor(df$campaign))
summary(factor(df$store))
table(df$campaign, df$store)
```

* There is an equal number of observations for each campaign: 142.  
* There is an uneven number of observations for each store.
  * Store E has the most observations: 105
  * Store A has the fewest observations: 23
* The table function breaks this down for each campaign/store combination.

## EDA (Overall)

Let's look at a visual representation of the data using a pairplot.

The code cell below creates a really useful set of plots for a dataset that is as small as this. We are only using the first four columns of data: __sales, adSPendFacebook, adSpendInstagram, campaign__. The __store__ column will not be included in this plot, but we could re-run it by setting color equal to store.

```{r}
# The ggpairs function is from the GGally package. It creates a rich pairplot
ggpairs(df
        , columns = 1:4 # Only include the first four columns,and leave out the last column, store.
        , aes(color = campaign # Let's look for any difference among campaign. 
              , alpha = .4 # Makes the colors partially transparent
              )
        )
```

### Organization of the pairplot
* The diagonal shows the univariate distribution for each variable.
  * For a numeric variable, a density plot is used, separated by campaign. 
  * For a categorical variable, a barplot is used to show the count of observations.
* The lower triangle shows bivariate relationships.
  * For two numeric variables, a scatter plot is used.
  * For a numeric and a categorical variable, a faceted histogram is used.
* The upper triangle quantifies bivariate relationships.
  * For two numeric variables, a correlation is used.
  * For a numeric and a categorical variable, a faceted boxplot is used.
  
### Takeaways from the pairplot
1. Sales for the campaign 3 are generally lower, as indicated in the distribution plots and box and whisker plots for sales in the first row of the pairplot.
2. Sales has a strong correlation with adSpendFacebook overall (`r round(cor(df %>% select(sales, adSpendFacebook))[2], 2)`). However, sales has a very high correlation with adSpendFacebook for campaign 1 (`r round(cor(df %>% filter(campaign == 'C1') %>% select(sales, adSpendFacebook))[2], 2)`), and a weak correlation with campaign 2 (`r round(cor(df %>% filter(campaign == 'C2') %>% select(sales, adSpendFacebook))[2], 2)`). You can kind of see these correlations in the scatter plot, but with so many colors, it's hard to verify.
3. Sales has a moderate correlation with adSpendInstagram overall (`r round(cor(df %>% select(sales, adSpendInstagram))[2], 2)`). Sales has a strong correlation with adSpendInstagram for campaign 2 (`r round(cor(df %>% filter(campaign == 'C2') %>% select(sales, adSpendInstagram))[2], 2)`) and campaign 3 (`r round(cor(df %>% filter(campaign == 'C3') %>% select(sales, adSpendInstagram))[2], 2)`), and a weak correlation with campaign 1 (`r round(cor(df %>% filter(campaign == 'C1') %>% select(sales, adSpendInstagram))[2], 2)`). You can kind of see these correlations in the scatter plot, but with so many data points, it's hard to verify.

## Campaign 1 (Backward Elimination)  

We will now illustrate steps 3-4 using the campaign 1.

3. Calculate results 
  * First using EDA: We will use scatter plots to look at bivariate relationships.  
  * Second using regression: We will use a backward elimination (top down) approach to create a model.
4. Tell others about the results: We will illustrate how to predict future sales using the prediction data, and then creating a plot of it.

### Calculate using EDA

Let's first create a scatter plot between adspend and sales for the first campaign.
```{r}
# Create a dataset only for the C1 campaign data
c1 <- df %>% filter(campaign == 'C1')

# Reshape the data from wide to long and then plot it
c1 %>%
  pivot_longer(cols = c(adSpendFacebook, adSpendInstagram)
               , names_to = 'ad', values_to = 'spend') %>%
  ggplot(aes(x = spend, y = sales, color = ad)) +
  geom_point()
```

This highlights the strong positive correlation between sales and adSpendFacebook for campaign 1. 

### Calculate using Regression

Let's use regression and use a backward elimination approach to creating a model that we can use for predicting sales from campaign 1.

Backward elimination is when you add in all the variables and then remove those that are insignificant.

#### Model 1

```{r}
lmc1_1 <- lm('sales ~ adSpendFacebook + adSpendInstagram + store', data = c1)
summary(lmc1_1)
```

__Observations__  

* Notice that R automatically detected that store is a categorical variable and so it created dummy variables to deal with that. Nice!
* The adjusted R-squared is high. This model would be good for making predictions.
* Should we remove any variables?  
  * The p-value on adSpendInstagram is insignificant. Thus, the coefficient is not reliably different from 0, and we should remove it from the model.
  * The p-values on the store coefficients are all insignificant. Thus, they have the same intercept, and should be removed from the model.
  * The final model that we present would be the one without the adSpendInstagram and store variables. 

#### Insignificance  

Let's represent the insignificance of the adSpendInstagram and store variables.

```{r}
# Reshape the data from wide to long and then plot it
c1 %>%
  pivot_longer(cols = c(adSpendFacebook, adSpendInstagram)
               , names_to = 'Platform', values_to = 'Spend') %>%
  ggplot(aes(x = Spend, y = sales, color = Platform)) +
  geom_point() +
  stat_smooth(method = 'lm', se = F) +
  facet_wrap(vars(store), ncol = 2)
```

__Observations__  
* The adSpendInstagram line is pretty flat in most of the plots. This means that it stays the same regardless of how much is spent, and is therefore insignificant.  
* The intercepts for adSpendFacebook are all about the same. There is a little variation in intercepts for the adSpendInstagram lines. This is why the store variable is insignificant.

### Back to model creation

#### Model 2

Let's create a simpler regression model by only including adSpendFacebook as a predictor variable.

```{r}
lmc1_2 <- lm('sales ~ adSpendFacebook', data = c1)
summary(lmc1_2)
```

__Observations__ 

* Notice that the adjusted R-squared is still very high, so this model could be reliably used for making predictions of what sales will be for campaign 1 based on how much you plan on spending for Facebook. This is also simpler.
* Specifically, we can see that each dollar spent on Facebook ads increases sales by about $`r round(coef(summary(lmc1_2))[2][1], 2)`.

### Predictions  

Let's make predictions with this model using the prediction data, and then visualize them in a 3d scatter plot using the plotly package.
```{r}
# Read in the prediction data
pd <- readRDS('predictionData.rds') # Explore it by clicking on the pd dataframe in the Environment pane.

# Create a new column of predicted sales using the lmsa2 model
pd$sales_pred <- predict(lmc1_2, pd)

# Create an interactive 3d scatter plot
plot_ly(data = pd
        , x = ~adSpendFacebook, y = ~adSpendInstagram, z = ~sales_pred
        , color = ~store
        , size = .5
        , type = 'scatter3d'
        , mode = 'markers'
)
```

__Observations__  

* If you orient the plot so that adSpendFacebook is in front, you can see that as you increase the amount spent on Facebook ads, the sales increases, as well. 
* If you orient the plot so that adSpendInstagram is in front, you can see that there is no relationship with sales. The observations fall everywhere.


## Campaign 2 (Forward Selection)  

Repeat this process with campaign 2, but using forward selection this time.

### Calculate Using EDA

Let's first create a scatter plot between adspend and sales for campaign 2.
```{r}
# Create a dataset only for the se campaign data
c2 <- df %>% filter(campaign == 'C2')

# Reshape the data from wide to long and then plot it
c2 %>%
  pivot_longer(cols = c(adSpendFacebook, adSpendInstagram)
               , names_to = 'Platform', values_to = 'Spend') %>%
  ggplot(aes(x = Spend, y = sales, color = Platform)) +
  geom_point()
```

It's hard to tell if either variable has a strong relationship with sales.

### Calculate Using Regression

I will use forward selection.

#### Model 1

```{r}
lmc2_1 <- lm('sales ~ adSpendFacebook', data = c2)
summary(lmc2_1)
```

**Observations**  
* The coefficient on adSpendFacebook is positive. I'll keep that variable, and add in another.

#### Model 2
```{r}
lmc2_2 <- lm('sales ~ adSpendFacebook + adSpendInstagram', data = c2)
summary(lmc2_2)
```

__Observations__  
* Both of the coefficients on adSpendFacebook and adSpendInstagram are significant. I'll keep those and add in store.  

#### Model 3

```{r}
lmc2_3 <- lm('sales ~ adSpendFacebook + adSpendInstagram + store', data = c2)
summary(lmc2_3)
```

__Observations__  

* The adjusted R-squared is really high. This model would be good for making predictions.
* Sales increase by about $5.24 for every dollar spent on advertisements on Facebook.
* Sales increase by about $14.02 for every dollar spend on advertisements on Instagram
* The store variable is very significant. Each store has a different intercept, except for store D. We will leave the store variable in the model.


### Predictions  

Let's make predictions with the lmc2_3 model using the prediction data, and then visualize them in a 3d scatter plot using the plotly package.
```{r}
# Create a new column of predicted sales using the lmc2_3 model
pd$sales_pred_lmc2_3 <- predict(lmc2_3, pd)

# Create an interactive 3d scatter plot
plot_ly(data = pd
        , x = ~adSpendFacebook, y = ~adSpendInstagram, z = ~sales_pred_lmc2_3
        , color = ~store
        , size = .5
        , type = 'scatter3d'
        , mode = 'markers'
)
```

__Observations__  

* It's easy to see that as you increase the amount spent on Instagram ads, the sales increase. Thus, you should allocate all advertising dollars to Instagram.  
* The intercept for stores B, C, and E are much different than for store A.


## Campaign 3  

Repeat this process with campaign 3. Use either backward elimination or forward selection.

### Calculate with EDA


### Calculate with Regression



#### Model 1


### Predictions  



